\LARGE \bf Can a toluene-degrading bacteria improve the growth of a bacterial community in case of toluene pollution?

### 2017-12-19 Data_csv/Paper/paper.tex
ss

Every surface, soil or liquid in our environment is colonized by multiple microorganisms, interacting with each other and forming communities. However, the whole complexity of the interactions is still today not always fully understood.
In addition, these communities also interact with other organisms and can be perturbed by the effects of pollution such as spillage of oil or solvent. We decided to use toluene as a pollutant for this experiment.

Toluene is an organic solvent widely used in industry nowadays, as a paint solvent or as extraction solvent in the cosmetic industry. Toluene is a monoaromatic volatile molecule which is toxic and ecotoxic \cite{toluene}. 
When such event happens, one way to treat it is the use of bioremediation. There are several different techniques of bioremediation but they all have the same purpose: to use live organisms to get rid of pollutants. The technique that interested us in this experiment was bioaugmentation, the addition of a microorganism able to degrade the targeted pollutant to a native community, allowing it to grow back \cite{Bioremediation}.

@@

Our hypothesis for this experiment were that the addition of PP or PV will have an effect on SC growth, especially in a toluene-only media, because we think that these strains might produce metabolites the SC could use as carbon source or reduce the toluene concentration and thus its toxic effect. This would lead to a better growth of SC in presence of one of either PP or PV.

\section{Material and method}

@@

\subsubsection{Pseudomonas veronii}
The growth of PV in each treatment is represented in Fig. \ref{aucpvw2} and \ref{PVgrowth2}.
As in the first week, there is an important difference of growth between the media (F = 784.71, df = 1, $p = 2.85 \cdot 10^{-9}$). PP grew about a hundred-fold better in toluene (red and orange) than in mixed carbon (black and blue curves/points).
One can also notice that PP grew slightly less in presence of SC, in both media (blue and yellow compared to black and red curves/points). The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$).While not being as significant as our other results, it could be an indication some competition between them in this type of culture. It seems plausible, knowing from previous experiments that PV grows a bit slower than PP and in this experiment some bacteria from the sand community were able to grow on toluene.
\newline

>>>>

Every surface, soil or liquid in our environment is colonized by multiple microorganisms, interacting with each other and forming communities. However, the whole complexity of the interactions still isn't fully understood today.
In addition, these communities also interact with other organisms and can be perturbed by the effects of pollution such as oil or solvent spillage. We decided to use toluene as a pollutant for this experiment.

Toluene is an organic solvent widely used in the paint or cosmetic industry nowadays. It is a monoaromatic volatile molecule which is toxic and ecotoxic \cite{toluene}. 
When such event happens, one way to treat it is the use of bioremediation. There are several different techniques of bioremediation but they all have the same purpose: to use live organisms to get rid of pollutants. The technique that interested us in this experiment was bioaugmentation, the addition of a microorganism able to degrade the targeted pollutant to a native community, allowing it to grow back \cite{Bioremediation}.

@@

Our hypothesis for this experiment were that the addition of PP or PV will have an effect on SC growth, especially in a toluene-only media, because we think that these strains might produce metabolites the SC could use as carbon source or reduce the toluene concentration and thus its toxic effect. This would lead to a better growth of SC in presence of either PP or PV.

\section{Materials and methods}

@@

\subsubsection{Pseudomonas veronii}
The growth of PV in each treatment is represented in Fig. \ref{aucpvw2} and \ref{PVgrowth2}.
As in the first week, there is an important difference of growth between the media (F = 784.71, df = 1, $p = 2.85 \cdot 10^{-9}$). PP grew about a hundred-fold better in toluene (red and orange) than in mixed carbon (black and blue curves/points).
One can also notice that PP grew slightly less in presence of SC, in both media (blue and yellow compared to black and red curves/points). The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$). While not being as significant as our other results, it could indicate some competition between them in this type of culture. It seems plausible, knowing from previous experiments that PV grows a bit slower than PP and in this experiment some bacteria from the sand community were able to grow on toluene.
\newline
